Approximate Bayesian Computation in Large Scale Structure: constraining the galaxy-halo connection

### 2017-02-24 ccppabc/text/main.tex
some further edits on the draft
ref comment #1 see pdf

{\bf \color{red} Overall, the constraints from ABC-PMC are consistent with those from 
the Gaussian pseudo-likelihood MCMC method; however, using ABC-PMC has a number of 
advantages. ABC-PMC utilizes a forward generative model. Our forward generative model, 
for instance, accounts for sample variance. In principle, they also have the advantage that they can account for sources of systematic uncertainties in the observational data. 
}

@@

Furthermore, the Gaussian-likelihood  approach relies on constructing an accurate covariance matrix
estimate that captures the sample variance of the data. While we are able to do this accurately 
within the scope of the HOD framework, for more general LSS parameter inference situations, it 
is both labor and computationally expensive and dependent on the accuracy of simulated mock catalogs,
which are known to be unreliable on small scales (see \citealt{cosmiccode,nifty} and references therein). 
Since ABC-PMC utilizes a forward model to account for sample variance, it does not depend on a 
covariance matrix estimate; hence it does not face these problems.

>>>>

{\bf \color{red} Overall, the constraints from ABC-PMC are consistent with those from 
the Gaussian pseudo-likelihood MCMC method; however, using ABC-PMC has a number of 
advantages. ABC-PMC utilizes a forward generative model. Our forward generative model, 
for instance, accounts for sample variance. Forward generative models also have the 
advantage that they can account for sources of systematic uncertainties that affect 
observational data.}

@@

{\bf \color{red} CHH: @MJV I'm not a big fan of this entire paragraph. The accuracy of the covariance
matrix depends on the accuracy of the mock catalogs (a.k.a. the forward model). While it's definitely 
true that on small scales they break down, forward models in ABC suffers from the same issues.} 
Furthermore, the Gaussian-likelihood  approach relies on constructing an accurate covariance matrix
estimate that captures the sample variance of the data. While we are able to do this accurately 
within the scope of the HOD framework, for more general LSS parameter inference situations, it 
is both labor and computationally expensive and dependent on the accuracy of simulated mock catalogs,
which are known to be unreliable on small scales (see \citealt{cosmiccode,nifty} and references therein). 
Since ABC-PMC utilizes a forward model to account for sample variance, it does not depend on a 
covariance matrix estimate; hence it does not face these problems.
